\section{Course Outline and Learning Objectives:}

	\begin{frame}{Course Learning Outcomes}
	  
	As a continuation of Web Technologies II, we will design and build Model View Controller pattern based Web applications using Node.js frameworks including Node Express Web Server and Angular JS Web Applications.  
	\begin{itemize}

	    \item Develop web applications that use a database as the back end model.
	    
	    \item Implement dynamic grid applications. The Node.js data grid library allows manipulating HTML tables with large data sets and provides extended features like advanced searches, custom sorts, complex conditional styles, custom filters, pagination and even line editing for your table. 
	\end{itemize}	    
	    
	\end{frame}	    
	
	\begin{frame}{Course Learning Outcomes}	
	\begin{itemize}	
	    \item Implement security protocols. The idea here is that Node.js applications are written in Modules. In fact, we have learned that all Computer Programs are written in smaller packages. We will study the steps we can take to prevent data injection attacks and other attempts by hackers to steal data from our applications. 
	    \item Develop applications that run on mobile devices. We will learn to use jQuery and the Bootstrap JS Framework to ensure that our applications render and display nicely on any device ours users interact on, from Apple Watches to Large Screen Displays.
	    
	\end{itemize}

		\emph{Our term project will be to design and build a Model View Controller application that includes client-side, server-side, and database processing.}	
		\end{frame}	  